Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/method.tex
[ADD] modules, changed titles

\subsection{Scientific Methodology} % Section

@@

Briefly, our web application will be tested with real users and unit tests, the system in general will be validated with benchmarks such as analyzing the its behavior and delays by growing the amount of users and data.

>>>>

%RP falta introdução à secção a explicar o que vai ser discutido aqui.

%RP texto que está nos 3 parágrafos seugintes ficava bem no planned schedule. Talvez esse fique melhor antes do evaluation methodology.

@@

\subsection{Evaluation Methodology} % Section

Our web application will be tested with real users, performance benchmarks and unit tests.

%RP elaborar o tipo de testes que vais fazer com os utilizadores: pedir para fazer tarefas e cronometrar o tempo que demoram. preencher questionários, decobrirem sozinhos como fazer algo, fazer após explicações, etc.

%RP detalhar os testes de desempenho de que falas.
The system in general will be validated with benchmarks such as analyzing its behavior and delays by growing the amount of users and data.
